\section{Market Potential}
\label{sect:market_potential}

%*********************
%Address the following:  Market analysis

% ********************
%Describe market potential, commercial promise, or open source value
%What is being provided
%Tools being used 
   %Barcode scanner
      %CSV
   %Database
      %SQL
      %Excell
   %Analytical and Development Service 

% ********************
%Evidence of user interest (provide references)
%Barcodes are a mainstream technology that almost every business uses
%There are cheap and efficient database services available today.
   %Monthly rental
   %Purchase your own server. 
   %Developers for databases.

%********************
%Competitive analysis
%Try to show:
   %that the group is providing a free service that has worth
%Database/software development. 

%********************************
%Notes on similar/related products (provide references)
%Identify direct and indirect competition
%Similar products: and entire website to all things barcode. https://www.barcodesinc.com/
   %Everything you need for any kind of barcode
   %even branches off into RFID
%Databsse rental and maintenance cost.
   %VMC may always have some one watching the system
      %Typically a work study or volunteer. 
%Database development
   %Project scope is fairly small
      %competition typically branches into software development. 

%**********************Competitive Advantage
%The leading edge on competitors is the customization that the project will have with it's clients.
%Time committal?

%****************Novelty of your solution, innovative characteristics
%The solution will help the VA help veterans by keeping track of them
   %That totally sounds like some big broth stuff.

%*********************What makes your solution better than the competition
%Currently no service on analyzing data to help veterans.
   %Our service personally caters to veterans and their welfare. 
%Putting lots of time into the project
   %Attention to detail / Pride of ownership

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       Market Potential Main Body       %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The project plan involves using a bar code scanner, to scan the bar codes on student identification cards. Bar codes are a mainstream technology that almost every business uses, and in this project bar code scanners are provided by the stake holders. In most cases of bar code use, the business has to spend money producing the bar codes. Think of how the post office prints a bar code for every piece of mail. However in VMC-TAP's case, the bar codes are already produced, at no cost to either the developer or the client.  VMC-TAP will be making software and a database software that uses bar code products. Software and database service for bar code technology has tremendous worth, as the software to operate identification card database can cost well over a hundred dollars~\cite{BARCODES_INC:2}. 


Database creation and analytical data analysis is another cost that can be compared to the work done by Knack. Knack is a software development company, with over 15 employees that specializes in database software and tools. They even provide a database service, that anyone can buy starting at forty dollars a month. They have some high profile customers like the Seattle Seahawks and the Salvation Army, as well as thousands of other clients. Knack and Barcodes, Inc claim to have an incredibly large customer base, clearly showing the market interest in customizable databases and software services that analyze data~\cite{KNACK:1}.
%evidence%

As a team of three, VMC-TAP provides a detailed and highly customizable service, that directly caters to the client's needs and request. No other company can relate to the VMC's customers better, while companies like Knack might be able to create a system faster, the VMC gains an invaluable insight by involving it's own customer base into developing important information gathering software. 

% EOF